Gamification Techniques in Collaborative Interactive Evolutionary Computation

### 2017-11-06 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-short-body.tex
old uncommitted changes

Interactive evolutionary computation (IEC) systems include persons in
a computational system performing different kind of tasks, which brings particular challenges
to their designers: human {\em computational cycles} are scarce, slow
and expensive to acquire, there is human 
fatigue caused by the interaction \cite{ie1}; besides, boredom arises
when users evaluate a large number of phenotypes. In this paper we
intend to solve these issues by developing a  human-centered 
\cite{gasson2003human} software framework that can be used to 
increase volunteer participation in C-IEC systems by using
gamification techniques, which are used to {\em human computational
  cycles} more abundant and possibly decrease boredom.

Gamification is the use of game design elements in non-game contexts \cite{deterding2011game}. 
The gamification element employed in this work is a rewarding mechanism
\cite{dubois2013understanding}. An example of the use of this technique is a recent
work by Wagy \& Bongard \cite{wagy2014collective} where user interaction is
needed for developing new designs of robot locomotion.
Collaboration is encouraged by gamifying the system using the maximum distance
indicator to inspire the user to try and ``beat'' previous designs. Also Seyama and
Munetomo \cite{seyama2016development} propose the reduction of user
fatigue by using a collaborative filtering algorithm to show only the
information utilized by similar users. In Section \ref{sec:framework}
we present our proposed framework. Next the EvoDrawings application case study 
is presented in Section \ref{sec:evodraw} and the
results are discussed in Section \ref{sec:results}. Finally, some concluding
remarks are provided in Section \ref{sec:conclusions}.

@@

A graph is proposed for modeling the social network of users and their interactions 
with candidate solutions, and the relationships between them in the population.
The graph database system used in the implementation is Neo4J, which is a scalable solution 
\cite{miller2013graph,holzschuher2013performance}. 
This graph is also used to increase engagement through gamification, as explained in the next section.

@@

\section{Results}
\label{sec:results} 
Before release, the deployment was first tried with a few beta testers. 
When applying the leader board gamification technique for the first time a 
problem was found: some users were cheating by giving a
rating to an animation even before it was returned from the server, this was done by just
constantly clicking the mouse button. This is a common problem found in systems using leader
boards because by making the scores visible to other players they are encouraged 
to compete \cite{hickman2010total}. The version used in experiments disabled the button until 
the drawing animation was over. The results of each of the three experiments in 
terms of participation are detailed next.

>>>>

Interactive Evolutionary Computation (IEC) systems include persons in
a computational system performing different kind of tasks, which brings particular challenges
to their designers: human {\em computational cycles} are scarce, slow
and expensive to acquire, there is human 
fatigue caused by the interaction \cite{ie1}; besides, boredom arises
when users evaluate a large number of phenotypes. In this paper we
intend to solve these issues by developing a  human-centered 
\cite{gasson2003human} software framework that can be used to 
increase volunteer participation in C-IEC systems by using
gamification techniques, which are used to {\em human computational
  cycles} more abundant and possibly decrease boredom.

Gamification is the use of game design elements in non-game contexts \cite{deterding2011game}. 
The gamification element employed in this work is a rewarding mechanism
\cite{dubois2013understanding}. An example of the use of this technique is a recent
work by Wagy \& Bongard \cite{wagy2014collective} in which interaction is
needed for developing new designs of robot locomotion.
Collaboration is encouraged by gamifying the system using the maximum distance
indicator to inspire the user to try and ``beat'' previous designs. Also 
Seyama \& Munetomo \cite{seyama2016development} propose the reduction of user
fatigue by using a collaborative filtering algorithm to show only the
information utilized by similar users. In Section \ref{sec:framework}
we present our proposed framework. Next, the EvoDrawings application case study 
is presented in Section \ref{sec:evodraw} and the
results are discussed in Section \ref{sec:results}. Finally, some concluding
remarks are provided in Section \ref{sec:conclusions}.

@@

A graph is proposed for modeling the social network of users and their interactions 
with candidate solutions and the relationships between them in the population.
The graph database system used in the implementation is Neo4J, which is a scalable solution 
\cite{miller2013graph,holzschuher2013performance}. 
This graph is also used to increase engagement through gamification, as explained in the next section.

@@

\section{Results}
\label{sec:results} 
Before release, the deployment was first tried with a few beta testers. 
When applying the leader board gamification technique for the first time, a 
problem was found: some users were cheating by giving a
rating to an animation even before it was returned from the server, this was done by just
constantly clicking the mouse button. Cheating is a common problem found in systems using leader
boards because by making the scores visible to other players they are encouraged 
to compete against each other \cite{hickman2010total}. The version used in experiments disabled the button until 
the drawing animation was over. The results of each of the three experiments in 
terms of participation are detailed next.
